\documentclass[10pt]{extarticle}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{color}
\usepackage{hyperref}

\usepackage[margin=0.25in]{geometry}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\usepackage{collectbox}
\DeclarePairedDelimiter\ceil{\lceils}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\usepackage{amsthm}
%opening
\title{
	Resume \\
}

\author{Daniel Joel Drake}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section] 

\theoremstyle{Definition}
\newtheorem{def.}{Definition}[section] 

\theoremstyle{Definition}
\newtheorem{prf}{Proof}[section] 

\theoremstyle{plain}
\newtheorem{exmp}{Example}[section]

\newcommand{\authordetailsblock}{
	\hspace{\fill} 
	\parbox[t]{0.48\textwidth}{ 
		\footnotesize 
		\Who\\ 
		\textit{\authordetails} 
	}
}

\begin{document}
	\twocolumn
	\maketitle		
	\noindent
	\section{Contact}
	\href{mailto:djd0011@uah.edu}{djd0011@uah.edu}  \\
	\href{mailto:danieldrake1@yahoo.com}{danieldrake1@yahoo.com}  \\
	Cell: 256-541-8526  \\
	Github: \href{https://github.com/Dragon121222}{https://github.com/Dragon121222} 
	\section{Education}
		\begin{itemize}
			\item Bachelor of Science from UAH.
			\begin{itemize}
				\item Major in Mathematics.
				\item Minor in Computer Science.
				\item Graduated December 6, 2018
		\end{itemize}
			\item Associates Degree from Calhoun Community Collage
			\begin{itemize}
				\item Major in Mathematics
				\item Graduated May 27, 2016
			\end{itemize}
		\end{itemize}
	\section{Previous Employment}
		Quantum Information Extraction \\
		Time: January 1st 2019 - March 27th 2020 \\ 
		Position: Electronics Engineer \\	 
		Contact: 
		\begin{itemize}
			\item Dr. Anthony Hester - ahester@qieinc.com - 256-684-0988
			\item Dr. Charles Hester - chester@qieinc.com - 256-651-3619
			\item Ricky Hammon - rhammon@qieinc.com - 256-476-5171
		\end{itemize}	
	Previous non-technical work available on request. 
	\section{Skills}
		\begin{itemize}
			\item \textbf{Graphics, Networking, and Camera Programming}
			\begin{itemize} 
				\item Blender, Unity with deployment to the Oculus Quest
				\begin{itemize}
					\item Precision models developed for 3D printing with application to prototyping and virtual reality environments. 
					\item Two unity games developed. One as a traditional 3D game. One as a VR game. 
				\end{itemize}
				\item C++ based OpenGL and GTK graphical user interfaces, game design, and machine learning interfaces
				\item High speed image and video processing design utilizing Arrayfire. 
				\begin{itemize}
					\item Real time - Fourier analysis based microscopic interferometric frequency detection applied to MEMS testing
				\end{itemize}					
				\item Video for linux 2 and UVC application designs
			\end{itemize}
			\item \textbf{Network Programming and Design}
			\begin{itemize}
				\item TCP, UDP, SQL, UART, SPI, I2C, and 
				JESD204B implementations with application to multiplayer games, general purpose networking including data management, and board to board communications
			\end{itemize}
			\item \textbf{FPGA design}
			\begin{itemize}
				\item Xilinx development using Vivado and ISE on the Virtex 7 written in Verilog
				\item High speed ADC control implementation
				\item High speed SFP networking control
			\end{itemize}
			\item \textbf{Custom Electronics designs}
			\begin{itemize}
				\item 10 Gb/s hardware design of optical - electrical media converter devices(SFP/SFP+ based Fiber, freespace, and ethernet interfaces)
				\item High voltage arbitrary function generation to control a fast steering mirrors
				\item Use and automation of Kicad and Eagle
			\end{itemize}			
			\item \textbf{High speed optical systems }
			\begin{itemize}
				\item Microscopic interfrometric system design
				\item Free space digital network design
			\end{itemize}
			\item \textbf{Security Systems Design}
			\begin{itemize}
				\item Real time intrusion detection based on Information theory and Algebraic Topological theory. 
				\item NIST 800-171 compliant system design
			\end{itemize}
			\item \textbf{Miscellaneous}
			\begin{itemize}
				\item Arduino and Raspberry Pi(2,3,4) programming as micro-controllers and RTOS
				\item Full stack website development
				\item Esoteric language experience
				\item Number theory and Calculus numerical approximation systems
				\item Operating system proficiency: Linux(Arch, Manjaro, Debian, Raspbian, Ubuntu, Fedora), Mac, and Windows
			\end{itemize}	
		\end{itemize}

\end{document}