\documentclass[12pt]{extarticle}
\usepackage{amsmath}
\usepackage{tikz}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{color}
\usepackage{hyperref}

\usepackage[margin=0.5in]{geometry}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\usepackage{collectbox}
\DeclarePairedDelimiter\ceil{\lceils}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\usepackage{amsthm}
%opening
\title{Business Architecture}
\author{Daniel Drake}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section] 

\theoremstyle{plain}
\newtheorem{axiom}{Axiom}[section] 

\theoremstyle{plain}
\newtheorem{lma}{Lemma}[section] 

\theoremstyle{Definition}
\newtheorem{def.}{Definition}[section] 

\theoremstyle{Definition}
\newtheorem{prf}{Proof}[section] 

\theoremstyle{Definition}
\newtheorem{quest}{Question}[section] 

\theoremstyle{plain}
\newtheorem{exmp}{Example}[section]

\theoremstyle{plain}
\newtheorem{ruleOfInference}{Rule Of Inference}[section]

\newcommand{\cut}[0]{\noindent\framebox[\linewidth]{\rule{\linewidth}{2pt}}\\}
\newcommand{\prof}[0]{	\noindent \textbf{Proof:} \rule{500pt}{2pt} \\ }

\newcommand{\ddash}{\boxed{\vdash}}

\begin{document}
	\maketitle
	
	\section{Roles and Relations and Responsibilities}

	\subsection{Roles}

	\begin{itemize}
		\item Market Research
		\item Legal
		\item Project Management
		\item Advertisement 
		\item Development 
		\item Testing
		\item Contract Negotiation 
		\item Sales
		\item Business Management	
		\item Support
	\end{itemize}
	
	\subsection{Market Research Relations and Responsibilities}
		\begin{itemize}
			\item To receive ideas generated by Development.
			\item To find out if there is an a demand for the product or service described by the idea. 
			\item To report the expected demand to Business Management.
		\end{itemize}
		\begin{def.} \textbf{Expected Demand} \\ \\
			The average temporal rate at which similar product or services are being sold and related min, max data, and curve data. \\
			The average monetary rate at which similar product or services are being sold and related min, max data, and curve data. \\
			The expect volume increase the market related to the product or service could sustain. \\
		\end{def.}
	\subsection{Legal Relations and Responsibilities}
		\begin{itemize}
			\item To receive ideas generated by Development. 
			\item To find out if there are any legal challenges which would need to be overcome in order to produce the product or service described by the idea. 
			\item To report an expected legal overhead both temporal and monetary to Business Management. 
			\item To manage the legal overhead in cooperation with Business and Project Management. 
		\end{itemize}
	\subsection{Project Management Relations and Responsibilities}
		\begin{itemize}
			\item To receive ideas generated by Development. 
			\item To generate a plans of action to accomplish ideas. 
			\item To deliver the plans of action to Business Management, Development, Testing, and Support 
			\item To receive updates from everyone. 
			\item To ensure that everyone stays on task and completes their responsibilities. 
			\item To report the status of all tasks to Business Management. 
		\end{itemize}
		\begin{def.} \textbf{Plan of Action} \\ \\
			An expected amount of time and resources required. \\ 
			A sequence and organization of steps required to accomplish the idea. 
		\end{def.}
	\subsection{Advertisement Relations and Responsibilities}
		\begin{itemize}
			\item To receive ideas generated by Development. 
			\item To generate and distribute propaganda about the ideas generated. 
			\item To report expected costs to Business Management. 
		\end{itemize}
	\subsection{Development Relations and Responsibilities}
		\begin{itemize}
			\item To develop ideas for products or services. 
			\item To report ideas to everyone. 
			\item To implement ideas which are chosen by Business management. 
			\item To locally test implementations as they are developed. 
			\item To report to Project Management as the steps to complete the plan of action are completed. 
		\end{itemize}
	\subsection{Testing}
		\begin{itemize}
			\item To comprehensively test the work developed by Development. 
			\item To demonstrate that tasks to be completed by Development have been accomplished. 
			\item To recreate problems reported by support. 
		\end{itemize}
	\subsection{Contract Negotiation}
		\begin{itemize}
			\item To establish a time frame in which a contract will be completed. 
			\item To establish the monetary compensation for the contracts completion. 
			\item To establish the scope of the contract. 
		\end{itemize}
	\subsection{Sales}
	\subsection{Business Management}
	\subsection{Support}		
\end{document}